Fast Automatic Bayesian Cubature Using Lattice Sampling

### 2019-07-23 BayesianCubaturePaper2018 - Rev1b.tex
rephrase the caption

\begin{figure}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2019-Jun-29}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
	\caption{Multivariate Gaussian probability estimated using Mat\'ern kernel with $d=2$ using the empirical Bayes stopping criterion. Top: Ratio of the integration error to the error tolerance versus execution time. Bottom: Execution time rapidly increases with increasing $n$. These figures can be reproduced using \code{matern\_guaranteed\_plots.m} in GAIL.}
	\label{fig:MVN_Metern_d2b2}
\end{figure}

>>>>

\begin{figure}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2019-Jun-29}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
	\caption{Multivariate Gaussian probability in $d=2$ estimated using Mat\'ern kernel and empirical Bayes stopping criterion. Top: Ratio of the integration error to the error-tolerance versus execution time. Bottom: Execution time rapidly increases with increasing $n$. These figures can be reproduced using \code{matern\_guaranteed\_plots.m} in GAIL.}
	\label{fig:MVN_Metern_d2b2}
\end{figure}
